\newcommand{\PHPamountofcolor}{75}
\newcommand{\SourceCodeContext}{5}
%Lets define the php language colors:
\definecolor{PHP_comment_old}{HTML}{FF8000}
\colorlet{PHP_comment}{PHP_comment_old!\PHPamountofcolor!black}
\definecolor{PHP_default_old}{HTML}{000000}
\colorlet{PHP_default}{PHP_default_old!\PHPamountofcolor!black}
\definecolor{PHP_keyword_old}{HTML}{6c9c11}
\colorlet{PHP_keyword}{PHP_keyword_old!\PHPamountofcolor!black}
\definecolor{PHP_emph1_old}{HTML}{0F58A2}
\colorlet{PHP_emph1}{PHP_emph1_old!\PHPamountofcolor!black}
\definecolor{PHP_emph2_old}{HTML}{CCAA00}
\colorlet{PHP_emph2}{PHP_emph2_old!\PHPamountofcolor!black}
\definecolor{PHP_emph4_old}{HTML}{C60484}
\colorlet{PHP_emph4}{PHP_emph4_old!\PHPamountofcolor!black}
\definecolor{PHP_string_old}{HTML}{C78F0A}
\colorlet{PHP_string}{PHP_string_old!\PHPamountofcolor!black}
\definecolor{PHP_variable_old}{HTML}{C82210}%C82210
\colorlet{PHP_variable}{PHP_variable_old!\PHPamountofcolor!black}
\definecolor{PHP_number_old}{HTML}{BF1CA6}
\colorlet{PHP_number}{PHP_number_old!\PHPamountofcolor!black}
%Now we want to highlight the variables. This will be done by triggering the function \PHPhighlightvar at the start of any $ run. This function wil only highlight variables and any other identifiers will be ignored. Luckily lstlisting will only give correct identifiers so we only will have to check if the previous call was made with a \usepackage{fontspec}

%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
%\usepackage{courier, textcomp}
\usepackage{etoolbox}
\newtoggle{InString}{}% Keep track of if we are within a string
\togglefalse{InString}% Assume not initally in string

\newcommand*{\ColorIfNotInString}[1]{\iftoggle{InString}{#1}{\color{PHP_number}#1}}%
%helper

\newcommand{\PHPhighlightvar}[1]{\ifnum\theDollarFlag=1 \color{PHP_variable} \fi#1\setcounter{DollarFlag}{0}}
\newcounter{DollarFlag}


\lstset{
  language        = php,
  basicstyle      = \footnotesize\ttfamily,
  keywordstyle    = \color{PHP_keyword},
  stringstyle     = \color{PHP_string!90!black}\toggletrue{InString},
  %this allows highlighting of variables:
  literate        =  {\$}{{\iftoggle{InString}{\$}{\setcounter{DollarFlag}{1}\color{PHP_variable}\$\color{PHP_default}}}}1
%    {"}{{{\ProcessQuote{"}}}}1% Disable coloring within double quotes
%    {'}{{{\ProcessQuote{'}}}}1% Disable coloring within single quote
    {0}{{{\ColorIfNotInString{0}}}}1
    {1}{{{\ColorIfNotInString{1}}}}1
    {2}{{{\ColorIfNotInString{2}}}}1
    {3}{{{\ColorIfNotInString{3}}}}1
    {4}{{{\ColorIfNotInString{4}}}}1
    {5}{{{\ColorIfNotInString{5}}}}1
    {6}{{{\ColorIfNotInString{6}}}}1
    {7}{{{\ColorIfNotInString{7}}}}1
    {8}{{{\ColorIfNotInString{8}}}}1
    {9}{{{\ColorIfNotInString{9}}}}1,
  identifierstyle = \color{PHP_default}\PHPhighlightvar,
  commentstyle    = \color{PHP_comment}\slshape,
  emph            =[1]{require_once, require, include_once, include, namespace, use, class, function, new},
  emphstyle       =[1]\color{PHP_emph1},%\bf,
  emph            =[2]{echo, empty, isset, array, instanceof},
  emphstyle       =[2]\color{PHP_emph2},%\bf,
  emph            =[3]{var, const, abstract, protected, private, public, static, final, extends, implements, global, if, else, foreach, for, endforeach, endif, endfor, elseif, as},
  emphstyle       =[3]\color{PHP_keyword},%\bf,
  emph            =[4]{return, throw, exit, __halt_compiler, continue, break},
  emphstyle       =[4]\color{PHP_emph4},%\bf,
  rulecolor       =\color{black},
  keywords    ={abstract, and, array, as, break, callable, case, catch, class, clone, const, continue, declare, default, die, do, echo, else, elseif, empty, enddeclare, endfor, endforeach, endif, endswitch, endwhile, eval, exit, extends, final, finally, for, foreach, function, global, goto, if, implements, include, include_once, instanceof, insteadof, interface, isset, list, namespace, new, or, print, private, protected, public, require, require_once, return, static, switch, throw, trait, try, unset, use, var, while, xor, yield,
  % laravel:
  references, on, onDelete, foreign, unsigned, primary, string, text, integer
  },
  breaklines = true,
  captionpos = b,
  %numbers=left,
  %stepnumber=1,
  %firstnumber=1,
  %numberfirstline=true,
  %numberstyle=\footnotesize,
  xleftmargin=0in,
  xrightmargin=0in,
  upquote=false,
  showlines=true,
  tabsize=1,
  literate={\ \ }{{\ }}1 % decrease space/tab size
  }